Estimating duration using survival analysis

### 2023-05-30 cis-perfect-testing.tex
various editing and figure creation

Consider a series of tests on the same individuals (longitudinal data), where some individuals have a series of positive tests.
We wish to estimate the distribution of time for which an individual is positive for.
An individual could have multiple infections, in which case we refer to "infection episodes", where each episode corresponds to a single infection event.

@@

@@

The reason for this approach, over modelling biomarkers (as in chapter\todo{ref chapter on ATACCC}) is...

The methods in this chapter deal with modelling two issues that arise from the data.
False negatives are not dealt with and left to chapter X.

The first issue is double interval censoring.
An event (either the initiating or terminating) is \emph{interval censored} if its value is only to lie within a range.
\emph{Double interval censoring} means both the initiating and the terminating events are interval censored.
The initiating event is censored because we only observe the change from being not detectable (i.e.: negative) at one test, to detectable (i.e.: positive) at the following test; at the terminating event we see the opposite occurring (see\todo{interval censoring figure}).

@@

\begin{figure}
\includegraphics[width=\textwidth]{cis-perfect-testing/images/likelihood_areas.jpg}
\todo[inline]{Digitalise figure of regions.}
\caption{Admissible, $\alpha_i$, inadmissible, $\beta_i$ and
untruncated, $\Omega_i^C$ regions for an episode $i$ in an
individual whose first test was at time 0 and negative, with subsequent
negative tests at times 7, 14, and 56, and positive tests at times 21
and 28. Purple region is $\alpha_i$, orange region (which includes all
negative infection times) is $\Omega_i^C$ and unshaded region is
$\beta_i$.\label{perf-test:fig:partitionSpace}}
\end{figure}

>>>>

Consider a series of tests on the same individuals (longitudinal data), where some individuals have a series of positive tests.
We wish to estimate the distribution of time for which an individual is positive for.
An individual could have multiple infections, in which case define \emph{infection episodes}, corresponding to a single infection event.

@@

Series of positive tests within CIS were heuristically categorised into episodes by Sarah Walker (see \autoref{episode-def}).
These tests are assumed to have been due to a single infection event.

@@

The reason for this approach, over modelling biomarkers (as in chapter\todo{ref chapter on ATACCC}) is...
\todo[inline]{Justify approach}

The methods in this chapter deal with modelling two issues that arise from the data.
False negatives are not dealt with and left to \autoref{imperf-test}.

The first issue is double interval censoring.
An event is \emph{censored} if the time of the event can only be bounded; it is \emph{left censored} if it is known to occur before a certain time, \emph{right censored} if it is known to occur after a certain time, and \emph{interval censored} if it is known to occur within an interval.
Censoring is a very widely studied problem, and a central consideration in any survival analysis.
Interval censoring arises in CIS because we only observe the change from being not detectable (i.e.: negative) at one test, to detectable (i.e.: positive) at the following test and vice versa; \textcite{bogaertsSurvival} review many statistical methods applicable to interval censoring (see \autoref{perf-test:fig:double-interval-censor}).
\emph{Double censoring} means that both the originating and terminating event are censored, and is also a well-studied problem, reviewed by \textcite{sunStatisticala}.
In CIS, we have \emph{double interval censoring} meaning that both the initiating and the terminating events are interval censored.
\begin{figure}
  \todo[inline]{Copy over figure demonstrating double interval censoring}
  \caption{Episodes data in CIS is double interval censored, meaning that both the start and end of the episode are only known up to an interval. \label{perf-test:fig:double-interval-censor}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{cis-perfect-testing/regions_diag}
\caption{Admissible, $\alpha_i$, inadmissible, $\beta_i$ and
untruncated, $\Omega_i^C$ regions for an episode $i$ in an
individual whose first test was at time 0 and negative, with subsequent
negative tests at times 7, 14, and 56, and positive tests at times 21
and 28. Purple region is $\alpha_i$, orange region (which includes all
negative infection times) is $\Omega_i^C$ and unshaded region is
$\beta_i$.\label{perf-test:fig:partitionSpace}}
\end{figure}
